Predicting sales of newly published books

### 2015-10-19 paper.tex
working in the results section (updating tables and comments)

%
% TODO: falta incluir aquí el análisis de los mapas SOM.
% Determinar las variables a usar, según el SOM
\textbf{ TODO: add the SOM analisys }
% una vez hecho, hay que hacer las ejecuciones para ese dataset.

@@

% Mean absolute error MAE / Root mean squared error RMSE /  Relative absolute error RAE / Root relative squared error RRSE
  % ¿Qué sentido tiene usar los 4 métodos de error? ¿Es que vamos a seleccionar uno? - JJ
  %[pedro] es lo habitual en los trabajos en los que se realizan tareas de predicción
  % en algunos calculan muchos más, pero estos son los más usados. 
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method 	& Time (sec.) 	      & MAE 		& RMSE 		& RAE (\%) & RRSE (\%) 		\\
\hline
  M5P 		& 2.94 $\pm$ 0.51 	  & 65.49 	& 133.73 	& 11.10 	 & 9.17 	  \\
\hline
  LR 		  & 0.33 $\pm$ 0.07 	  & 100.813 & 257.63 	& 17.09 	 & 17.67 	\\
\hline
  SVM 		& 49.10 $\pm$ 8.05	  & 52.30	  & 139.45	& 8.87     & 9.56  	\\
\hline
  kNN 		& 0.03 $\pm$ 0.01 	  & 198.16 	& 542.93 	& 33.59 	 & 37.24 	\\
\hline
  MLP 		& 12.70 $\pm$ 3.08 	  & 97.18 $\pm$ 24.74 	& 174.77 $\pm$ 31.50 	& 16.47 $\pm$ 4.19 	& 11.99 $\pm$ 2.16 	\\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different
    forecasting methods on the original dataset (16 variables per book).}} 
\label{tabla:resultsT}
\end{table*}

@@

\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%)  & RRSE (\%)      \\
\hline
  M5P     & 7.77 $\pm$ 1.15     & 117.78  & 260.05  & 18.51     & 17.00  \\
\hline
  LR      & 41.72 $\pm$ 8.41    & 120.29  & 252.91  & 18.91     & 16.54   \\
\hline
  SVM     & 1652.20 $\pm$ 283.50& 109.30  & 251.16   & 17.18    & 16.42   \\
\hline
  kNN     & 0.03 $\pm$ 0.01     & 293.98  & 1071.52  & 46.21    & 70.06   \\
\hline
  MLP     & 3643.59 $\pm$ 72.40 & 696.92 $\pm$ 85.38 & 1609.37 $\pm$ 76.44  & 108.54 $\pm$ 13.34  & 105.96 $\pm$ 4.93   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset with 9 variables per book.}}
\label{tabla:results9}
\end{table*}

@@

\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%)  & RRSE (\%)      \\
\hline
  M5P     & 7.77 $\pm$ 1.15     & 117.78  & 260.05  & 18.51     & 17.00  \\
\hline
  LR      & 41.72 $\pm$ 8.41    & 120.29  & 252.91  & 18.91     & 16.54   \\
\hline
  SVM     & 1652.20 $\pm$ 283.50& 109.30  & 251.16   & 17.18    & 16.42   \\
\hline
  kNN     & 0.03 $\pm$ 0.01     & 293.98  & 1071.52  & 46.21    & 70.06   \\
\hline
  MLP     & 3643.59 $\pm$ 72.40 & 696.92 $\pm$ 85.38 & 1609.37 $\pm$ 76.44  & 108.54 $\pm$ 13.34  & 105.96 $\pm$ 4.93   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset with 4 variables per book.}}
\label{tabla:results4}
\end{table*}

% - indicar que el uso de las dos variables categóricas hace más difícil de aprender el conjunto
Paying attention to the obtained results shown in tables \ref{tabla:results13} 
and \ref{tabla:results7}, using those categorical variables as part of a big 
data set makes the problem hard to solve, both in required time to build the 
forecasting models as well as in the obtained errors.
However, as stated before, Trevenque expert sales manager, taking into account 
his knowledge in industry experience and their perceptions, decided that 
\emph{EDITORIAL} and \emph{SUBJECT} should be taken into account.

@@

Taking into account the SVM model obtained results, this method obtains the lower 
%FERGU: "the best errors" no se sabe si es lo mejor o lo peor xDD Pon "worst results" o así
errors. Even when used using the default parameter values it exhibit a good 
generalization performance.
However, it is much slower than the others to build the model, not only when 
using the data set with 13 input variables, but when using the data set with %FERGU: a veces pones dataset: unificarlo
7 input variables (including \emph{EDITORIAL} and \emph{SUBJECT}).

@@

As far as the Multilayer Perceptron, its main drawbacks are both the cost of model 
building (not only parameter and weights setting, but also time to train the 
network) and the fact that it is a back-box model, and thus, it is difficult 
to explain how the forecasts are obtained.
In these experiments, the MLP requires a higher time than other methods, but also
the obtained errors are worse as no parameter tuning to build the models have
been carried out.
Also, the difficulty to process information related to variables \emph{EDITORIAL} 
and \emph{SUBJECT} might affect the worse results obtained on the final dataset.

>>>>

%
% TODO: falta incluir aquí el análisis de los mapas SOM.
%*************************************** Determinar las variables a usar, según el SOM
\textbf{ TODO: add the SOM analisys }
% una vez hecho, hay que hacer las ejecuciones para ese dataset.

@@

% Mean absolute error MAE / Root mean squared error RMSE /  Relative absolute error RAE / Root relative squared error RRSE
  % ¿Qué sentido tiene usar los 4 métodos de error? ¿Es que vamos a seleccionar uno? - JJ
  %[pedro] es lo habitual en los trabajos en los que se realizan tareas de predicción
  % en algunos calculan muchos más, pero estos son los más usados. 
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method 	& Time (sec.) 	      & MAE 		& RMSE 		& RAE (\%) & RRSE (\%) 		\\
\hline
  M5P 		& 23.13 $\pm$ 4.22    & 197.48  & 577.28  & 35.21    & 41.85  \\
\hline
  LR 		  & 3327.87 $\pm$ 607.58& 247.22 & 561.67  & 44.08    & 40.71    \\
\hline
  SVM 		& 5425.68 $\pm$ 990.59& 215.69  & 574.76  & 38.46    & 41.66  \\
\hline
  kNN 		& 0.02 $\pm$ 0.00     & 302.07 	& 924.94 	& 53.86 	 & 67.05 	\\
\hline
  MLP 		& - 	  & - 	& - 	& - 	& - 	\\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different
    forecasting methods on the original dataset (16 variables per book). 
    In this case, due to the categorial variables, the MLP could not be run.}} 
\label{tabla:resultsT}
\end{table*}

%***************************************
\textbf{ TODO: add the table of results obtained using the variables selected taking into account the SOM analysis }

@@

\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%) & RRSE (\%)      \\
\hline
  M5P     & 2.27 $\pm$ 0.02     & 195.97  & 629.33  & 34.94    & 45.62  \\
\hline
  LR      & 0.38 $\pm$ 0.01     & 256.19  & 549.19  & 45.68    & 39.81   \\
\hline
  SVM     & 132.64 $\pm$ 2.86   & 230.66  & 613.27  & 41.12    & 44.45   \\
\hline
  kNN     & 0.06 $\pm$ 0.01     & 214.76  & 551.33  & 38.29    & 39.96   \\
\hline
  MLP     & 130.77 $\pm$ 1.51   & 326.60 $\pm$ 75.77 & 687.61 $\pm$ 55.70  & 58.23 $\pm$ 13.51  & 49.84 $\pm$ 4.04   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset with 9 variables per book.}}
\label{tabla:results9}
\end{table*}

@@

\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%)  & RRSE (\%)      \\
\hline
  M5P     & 2.02 $\pm$ 0.01     & 205.52  & 556.90  & 36.64     & 40.37  \\
\hline
  LR      & 0.32 $\pm$ 0.00     & 261.04  & 547.42  & 46.54     & 39.68   \\
\hline
  SVM     & 81.74 $\pm$ 1.66    & 242.26  & 606.07   & 43.19    & 43.93   \\
\hline
  kNN     & 0.05 $\pm$ 0.00     & 216.05  & 506.34  & 38.52    & 36.70   \\
\hline
  MLP     & 47.80 $\pm$ 0.51    & 318.29 $\pm$ 43.96 & 587.50 $\pm$ 51.50  & 56.75 $\pm$ 7.84  & 42.59 $\pm$ 3.73   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset with 4 variables per book.}}
\label{tabla:results4}
\end{table*}

% - indicar que el uso de las dos variables categóricas hace más difícil de aprender el conjunto
Paying attention to the obtained results shown in tables \ref{tabla:resultsT}, 
\ref{tabla:results9} and \ref{tabla:results4}, using those categorical variables 
as part of a big data set makes the problem hard to solve, both in required 
time to build the forecasting models as well as in the obtained errors.
Moreover, some methods are unable to build the models in a reasonable time.
%However, as stated before, Trevenque expert sales manager, taking into account 
%his knowledge in industry experience and their perceptions, decided that 
%\emph{EDITORIAL} and \emph{SUBJECT} should be taken into account.

@@

Taking into account the SVM model obtained results, this method obtains the lower 
errors. Even when used using the default parameter values it exhibit a good 
generalization performance.
However, it is much slower than the others to build the model, not only when 
using the dataset with categorical input variables, but also when using the 
datasets with numerical variables.

@@

As far as the Multilayer Perceptron, its main drawbacks are both the cost of model 
building (not only parameter and weights setting, but also time to train the 
network) and the fact that it is a back-box model, and thus, it is difficult 
to explain how the forecasts are obtained.
Moreover, in these experiments it has been seen the difficulty to process 
information related to categorial variables, such as \emph{editorial} and 
\emph{collection}.
